Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-04 paper.tex
Respond to review concerning perfectly known environments.

\textbf{In this paper, we present a planning algorithm that considers exact models of a humanoid
robot and its environment. It is used to solve navigation and manipulation problems. Our planner 
generates collision-free, statically balanced
geometric paths, i.e. paths such that for any path configurations, the robot is balanced on its
feet with zero speed. We also present a constructive formal proof that these paths can be
approximated by collision-free, dynamically balanced walk trajectories, i.e. trajectories such
that for any trajectory instant, the robot is balanced on at least one foot.} Our planner is designed for indoor
environments, where the floor is horizontal and flat. Because we do not compute explicitly footstep
positions at the planning stage, the presented planner is unable to plan motions in which the
robot steps over obstacles. This limitation is discussed in the paper.

@@

The presented experiment setup assumes perfect knowledge of the environment. This can
be guaranteed during experiments by using calibrated objects and motion capture systems.
This allows us to focus on complex motion planning problems. The perception problem,
interesting as it is, is completely decoupled from the planning problem in our
presentation.

@@

The presented setup also assumes perfect execution of the plan. It can be 
critical here, since
non-nominal stepping may cause to drift away from the planned trajectory. Future 
experiments will  include trajectory following during plan execution.

>>>>

\textbf{In this paper, we present a planning algorithm that considers exact models of a humanoid
robot and its environment. It is used to solve navigation and manipulation problems. Our planner 
generates collision-free, statically balanced
geometric paths, i.e. paths such that for any path configurations, the robot is balanced on its
feet with zero speed. We also present a constructive formal proof that these paths can be
approximated by collision-free, dynamically balanced walk trajectories, i.e. trajectories such
that for any trajectory instant, the robot is balanced on at least one foot. Our planner is designed for perfectly modeled indoor
environments, where the floor is horizontal and flat. Also, because we do not compute explicitly footstep
positions at the planning stage, the presented planner is unable to plan motions in which the
robot steps over obstacles. These limitations are discussed in the paper.}

@@

\textbf{The presented experiment setup assumes perfect knowledge of
  the environment. This can be guaranteed during experiments by using
  calibrated objects and motion capture systems. This indeed allows us
  to focus on complex motion planning problems. The perception
  problem, interesting as it is, is thus completely decoupled from the
  planning problem in our presentation.}

\textbf{The constrained motion planner and the small-space
  controllability property can luckily still be used with different
  environment representations that might more suited with perception
  systems and their inherent measurement errors, using for instance
  point clouds. In the future, we would like to achieve dynamic walk
  planning using a Kinect sensor that would be mounted on the humanoid
  robot. This would relax the a priori environment knowledge
  constraint and bring us one step closer to reactive planning in
  unknown environments.}

@@

The presented setup also assumes perfect execution of the plan. It can
be critical here, since non-nominal stepping may cause the robot to
drift away from the planned trajectory. Future experiments will
include trajectory following during plan execution.
